Comment on Cumulative Excess Deaths in New Zealand in the COVID-19 Era: Biases from Ignoring Changes in Population Growth Rates

### 2024-07-12 rawfiles/README.qmd
explained how to download excel file

While the data files and R code for generating the results and figures is available in the support folder, as not everyone is familiar with R, I am also providing an [Excel file in the supportFiles](supportFiles/ASMR_in_Excel.xlsx) folder which implements the normal Age Standardised Mortality steps so that people can review and test the logic themselves. It shows the steps of:

>>>>

While the data files and R code for generating the results and figures is available in the support folder, as not everyone is familiar with R, I am also providing an [Excel file in the supportFiles](supportFiles/ASMR_in_Excel.xlsx) folder (use the download raw files button in the upper right) which implements the normal Age Standardised Mortality steps so that people can review and test the logic themselves. It shows the steps of:
